Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-11-15 WSSSPE3/report/wg_main_industry_interaction.tex
very tiny changes

Although transitions are often studied under the broad umbrella of ``technology
transfer'', we believe there are likely to be a number of different ways in which
a pathway from initial production to long-term maintenance and secure funding are
achieved. In short, industry sponsorship is an important aspect of sustaining
scientific software, but our current understanding of these transitions focuses
narrowly on commercial successes\slash failures.

@@

\item Pathway to Impact - UK report: two pages of grant proposals are asked to
forecast how they might impact (includes environmental, academic, economic) \choinote{say impact on what?}.

>>>>

Although transitions are often studied under the broad umbrella of ``technology
transfer,'' we believe there are likely to be a number of different ways in which
a pathway from initial production to long-term maintenance and secure funding are
achieved. In short, industry sponsorship is an important aspect of sustaining
scientific software, but our current understanding of these transitions focuses
narrowly on commercial successes\slash failures.

@@

\item Pathway to Impact - UK report: two pages of grant proposals are asked to
forecast what impact they might have (including environmental, academic, economic).
